SemanticPaint

### 2015-12-06 cv3d_seminar/presentation.tex
add section seprator slide
all but SRF and Related

\documentclass[mathserif, 8pt]{beamer}
\input{macro}

@@

\setbeamertemplate{frametitle}{
	\vskip30pt
 	\usebeamercolor[blue!60!green]{frametitle}
  	\centering
  	\insertframetitle
	\vskip5pt
	\color{blue!60!green}{\hrule}
	}
}

\setbeamercolor{math text}{fg=orange!80!black}
\newcommand{\hl}[1]{\textcolor{red!80!black}{\underline{#1}}}

@@

%---------------------------------------------------------------------------------------
\section{State of the Art}
\begin{frame}
\frametitle{Introduction}

@@

%---------------------------------------------------------------------------------------
\section{Pipeline}
\begin{frame}
\frametitle{Introduction}

@@

 \begin{column}{0.5\textwidth}
  Data:\\
  300 objects\\
  51 classes\\
  full revolution\\
  3 points of view \\
  \vspace{0.5cm}
  SRF - Streaming Random Forest\\
  ORF - Online Random Forest\\
  HT - Hoeffding Tree \\
 \end{column}
\end{columns}

@@

%---------------------------------------------------------------------------------------
\section{Discussion and Outlook}
\begin{frame}
\frametitle{Summary}

@@

\begin{frame}
\frametitle{Failures}

@@

\begin{frame}
\frametitle{Future Work}

\begin{frame}
\frametitle{Two columns}
\begin{columns}[t]
\begin{column}{0.45\linewidth}
Left
\end{column}
\begin{column}{0.45\linewidth}
Right
\end{column}
\end{columns}
\end{frame}

%---------------------------------------------------------------------------------------
\begin{frame}
\frametitle{How to include an image}
\begin{center}
\includegraphics[width=0.3\linewidth]{template}
\end{center}
\end{frame}

>>>>

\documentclass[mathserif, 10pt]{beamer}
\input{macro}

@@

\setbeamertemplate{frametitle}{
	\vskip30pt
 	\usebeamercolor[blue!60!green]{frametitle}
  	\centering
  	\insertframetitle
	\vskip5pt
	\color{blue!60!green}{\hrule}
	}
}
\setbeamertemplate{footline}[frame number]
\setbeamercolor{math text}{fg=orange!80!black}
\newcommand{\hl}[1]{\textcolor{red!80!black}{\underline{#1}}}

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

@@

%---------------------------------------------------------------------------------------
\section{State of the Art}
\begin{frame}
\frametitle{Acquisition and Reconstruction}

@@

\begin{frame}
\frametitle{Scene Understanding}

%---------------------------------------------------------------------------------------
\section{Pipeline}
\begin{frame}
\frametitle{Voxel Oriented Patch features}

\begin{columns}
 \begin{column}{0.5\textwidth}
  \begin{figure}
  \center
  \includegraphics[width=\textwidth]{figures/vop}
  \caption{Colours shown in RGB for illustration purposes.}
  \label{fig:vop}
\end{figure}
 \end{column}
 \begin{column}{0.5\textwidth}
    $(\mathbf{p} - \mathbf{p}_i) \cdot \mathbf(n)_i = 0$ \\
    $r \times r$, $r = 13px$ with $10\frac{mm}{pixel}$\\
    CIELab\\
    Rotated to dominant gradient direction

 \end{column}

\end{columns}
\end{frame}

\begin{frame}
\frametitle{Streaming Random Forest}
\end{frame}

\begin{frame}
\frametitle{SRF - Reservoir Splitting}

\begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/forest}
%   \caption{Splitting reservoirs in Streaming Random Forest.}
  \label{fig:forest}
\end{figure}

\begin{frame}
\frametitle{Dynamic Conditional Random Field}

  \begin{equation} \label{eq:posterior}
  P(\mathbf{x}|\mathbf{D}) = \prod_{i \in \mathcal{V}} \left( \psi_i(x_i) \prod_{j \in \mathcal{E}_i} \psi_{ij}(x_i, x_j) \right) 
  \end{equation}

  \begin{equation} \label{eq:energy}
  E_t(\mathbf{x}) = \sum_{i \in \mathcal{V}} \left( \phi_i(x_i) + \sum_{j \in \mathcal{E}_i} \phi_{ij} (x_i, x_j) \right) + K
  \end{equation}

\begin{frame}
\frametitle{CRF - User Interactions}

  Touching:
  \begin{equation}
  \phi_i(l) =
    \begin{cases}
      0      & \quad \text{if } l = l_S\\
      \infty  & \quad \text{otherwise}\\
    \end{cases}
  \end{equation}

  Encircling:
  \begin{equation}
  \phi_i(l) =
    \begin{cases}
      \log P_E(fg|\mathbf{a}_i)       & \quad \text{if } l = \text{fg}\\
      \log (1 - P_E(fg|\mathbf{a}_i))  & \quad \text{if } l = \text{bg}\\
    \end{cases}
  \end{equation}

\begin{frame}
\frametitle{CRF - Predictions and Smoothnes}

  Predictions:
  \begin{equation}
  \phi_i(l) = -\log P_F(x_i = l | \mathbf{D})
  \end{equation}

  Smoothnes:
  \begin{equation}
      \phi_{ij}(x_i, x_j)  = \theta_p e^{-||\mathbf{p}_i - \mathbf{p}_j||}  + \theta_a e^{-||\mathbf{a}_i - \mathbf{a}_j||} + \theta_n e^{-||\mathbf{n}_i - \mathbf{n}_j||}
  \end{equation}
\end{frame}

\begin{frame}
\frametitle{Mean-Field Inference}
$P(\mathbf{x})$ approximated by $Q(\mathbf{x})$ under $KL(Q||P)$:
\begin{equation}
 Q_i^t(l) = \frac{1}{Z_i}e^{M_i(l)} \text{, } t = 1, \ldots, T
\end{equation}
\begin{equation}
 M_i(l) = \phi_i(l) + \sum_{l' \in \mathcal{L}} \sum_{j \in \mathcal{N}(i)} Q_j^{t-1}(l')\phi_{ij}(l, l')
\end{equation}

Frame at time $t$ initialized with:
\begin{equation}
 \widetilde{Q}_i^t(x_i) = \gamma Q_i^{t-1}(x_i) + (1 - \gamma) P_F^{t-1}(x_i = l | \mathbf{D}) \text{, } \gamma \in [0, 1]
\end{equation}

@@

 \begin{column}{0.5\textwidth}
  Data:\\
  300 objects\\
  51 classes\\
  full revolution\\
  3 points of view \\
  \vspace{0.5cm}
  SRF - Streaming Random Forest\\
  ORF - Online Random Forest\\
  HT - Hoeffding Tree \\
 \end{column}
\end{columns}
\end{frame}

%---------------------------------------------------------------------------------------
\section{Discussion and Outlook}
\begin{frame}
\frametitle{Summary}
\begin{itemize}
 \item customized models of 3D enviornments
 \item fully interactive
 \item online and real time
 \item no pretraining
\end{itemize}

@@

\begin{frame}
\frametitle{Failures}
\begin{columns}
 \begin{column}{0.5\textwidth}
  \begin{figure}[!ht]	 
  \center
  \includegraphics[width=\textwidth]{figures/failures}
  \caption{Failure cases.}
  \label{fig:failures}
  \end{figure}
 \end{column}

 \begin{column}{0.5\textwidth}
  \begin{itemize}
   \item bleeding
   \item illumination change
   \item viewpoint change
  \end{itemize}
 \end{column}
\end{columns}

@@

\begin{frame}
\frametitle{Future Work}
\begin{itemize}
 \item class priors for different enviornments
 \item priors for class properties (vertical walls)
 \item discriminative geometrical features
 \item outdoor enviornments
 \item better scalability
\end{itemize}

@@
